### 2018-12-13 tex/paper.tex
Pawan's corrections made for Potts model.

\mysubsection{Potts Model}
The Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. 
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\begin{proof}
In the limit of $T \to 0$, we can rewrite the above problem as
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \max_{i} (-s_{ai}).
\end{equation}
In vector form, the problem becomes
\begin{align}
    &\min_{{\bf s} \in EP(F)} \max_{{\bf y} \in \Delta} - \langle {\bf y}, {\bf s} \rangle \\
    & = - \max_{{\bf s} \in EP(F)} \min_{{\bf y} \in \Delta} \langle {\bf y}, {\bf s} \rangle
    \label{eq:maxmin}
\end{align}
$\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \succeq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\}
    \label{eq:delta2}
\end{equation}
where ${\bf y}_a$ is the component of $\bf y$ corresponding to the $a$-th variable. By the minimax theorem for LP, we can reorder the terms:
\begin{equation}
    - \min_{{\bf y} \in \Delta} \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle 
    \label{eq:minmax}
\end{equation}
Recall that $\max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle$ is the value of the Lovasz extension of $F$ at $\bf y$, that is, $f({\bf y})$. Hence, as $T \to 0$, the marginal inference problem converts to minimising the Lovasz extension under the simplices constraint:
\begin{equation}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
    \label{eq:minLovasz}
\end{equation}
\end{proof}

@@

The question now becomes how to recover the worst-case optimal submodular extension using $E({\bf y})$. The following propositions answers this question.
{\proposition The worst-case optimal  submodular extension for Potts model is given by $F_{Potts}(A) = \sum_{i = 1}^L F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} \frac{w_{ab}}{2} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
Also, $E({\bf y})$ in (P-LP) is the Lovasz extension of $F_{Potts}$.
\label{proposition:potts_worst-case optimal}}
\begin{proof}
Since $F_{Potts}$ is sum of Ising models $F_i$, we first focus on a particular label $i$ and then generalize. Consider a graph with only two variables $X_a$ and $X_b$ with an edge between them. The ground set in this case is $\{v_{ai}, v_{bi}\}$. Let the corresponding relaxed indicator variables be ${\bf y} = \{y_{aj}, y_{bj}\}$, such that $y_{ai}, y_{bi} \in [0, 1]$ and assume $y_{ai} > y_{bi}$. The Lovasz extension in this case is:

>>>>

\mysubsection{Pairwise Potts Model}
The pairwise Potts model, also known as the uniform metric, specifies the pairwise potentials $\phi_{ab}(x_a, x_b)$ in equation (\ref{eq:energy_min}) as follows:
\begin{equation}
    \phi_{ab}(x_a, x_b) = w_{ab} \cdot [x_a \neq x_b],
\end{equation}
where $w_{ab}$ is the weight associated with edge $(a, b)$. There are no higher-order potential terms in this model as in equation (\ref{eq:energy_min}).
%
\myparagraph{Tightest LP Relaxation} Before describing our set encoding and submodular extension, we briefly outline the LP relaxation of the corresponding MAP estimation problem. To this end, we define indicator variables $y_{ai}$ which equal 1 if $X_a = i$, and 0 otherwise. The following LP relaxation is the tightest known for Potts model in the worst-case, assuming the Unique Games Conjecture to be true \citep{manokaran2008sdp}
\begin{align}
    \text{(P-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a} \sum_{i} \phi_a(i)y_{ai} + \nonumber\\
     &\sum_{(a, b) \in {\mathcal N}} \sum_{i} \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:p-lp}
\end{align}
The set $\Delta$ is the union of $N$ probability simplices:
\begin{equation}
    \Delta = \{{\bf y}_a \in \mathbb{R}^L | {\bf y}_a \geq 0  \textrm{ and } \langle {\bf 1}, {\bf y}_a \rangle = 1\},
    \label{eq:delta}
\end{equation}
where $\bf y$ is the vector of all variables and ${\bf y}_a$ is the component
of $\bf y$ corresponding to $X_a$.

@@

\begin{proof}
In the limit of $T \to 0$, we can rewrite the above problem as
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad \sum_{a = 1}^{N} \max_{i} (-s_{ai}).
\end{equation}
In vector form, the problem becomes
\begin{align}
    &\min_{{\bf s} \in EP(F)} \max_{{\bf y} \in \Delta} - \langle {\bf y}, {\bf s} \rangle \\
    & = - \max_{{\bf s} \in EP(F)} \min_{{\bf y} \in \Delta} \langle {\bf y}, {\bf s} \rangle
    \label{eq:maxmin}
\end{align}
where $\Delta$ is the domain as defined as in equation (\ref{eq:delta}). By the minimax theorem for LP, we can reorder the terms:
\begin{equation}
    - \min_{{\bf y} \in \Delta} \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle 
    \label{eq:minmax}
\end{equation}
Recall that $\max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle$ is the value of the Lovasz extension of $F$ at $\bf y$, that is, $f({\bf y})$. Hence, as $T \to 0$, the marginal inference problem converts to minimising the Lovasz extension under the simplices constraint:
\begin{equation}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
    \label{eq:minLovasz}
\end{equation}
\end{proof}

@@

The question now becomes how to recover the worst-case optimal submodular extension using $E({\bf y})$. The following proposition answers this question.
{\proposition The worst-case optimal  submodular extension for Potts model is given by $F_{Potts}(A) = \sum_{i = 1}^L F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} \frac{w_{ab}}{2} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
Also, $E({\bf y})$ in (P-LP) is the Lovasz extension of $F_{Potts}$.
\label{proposition:potts_worst-case optimal}}
\begin{proof}
Since $F_{Potts}$ is sum of Ising models $F_i$, we first focus on a particular label $i$ and then generalize. Consider a graph with only two variables $X_a$ and $X_b$ with an edge between them. The ground set in this case is $\{v_{ai}, v_{bi}\}$. Let the corresponding relaxed indicator variables be ${\bf y} = \{y_{aj}, y_{bj}\}$, such that $y_{ai}, y_{bi} \in [0, 1]$ and assume $y_{ai} > y_{bi}$. The Lovasz extension in this case is:
